---
title: "Assessment 1.2"
author: "Kishan Goonewardane"
date: "22/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Question 2 - Create the heading of the first level and call it Data wrangling
# Data Wrangling 

Question 3 - Insert an R chunk and create a variable with this dataset
```{r} 

install.packages("tidyverse")

fastfood<-read.csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')

install.packages('skimr')
  
```



Question 4 - Show the number of observations for each restaurant.

```{r}

fastfood%>%count(restaurant)
```


Question 5 - Calculate and display the average number of calories for each restaurant.

```{r}

fastfood%>%group_by(restaurant)%>%summarise(avarage_calories=mean(calories))%>%ungroup()

```



Question 6 - Add a variable to the dataset, which calculates the average calories per type of restaurant and call it `average_calories`

```{r}

avarage_calories<-fastfood%>%group_by(restaurant)%>%summarise(avarage_calories=mean(calories))%>%ungroup()

```



Question 7 - Display the data vis of total fat per each type of restaurant. Write a narration (2-3 sentences) why you believe this type of data viz presents such information best. **

```{r}

fastfood%>%ggplot(aes(total_fat))+geom_histogram()+facet_wrap(vars(restaurant))

```
When presenting data to a wider audience, it is always beneficial to present the data in a visual manner. This allows the presenter gauge the attention of the audience and present the data in a timely manner. 



Question 8 - Display the count of observations per each type of restaurant
 

```{r}

fastfood%>%ggplot(aes(total_fat))+geom_histogram()

```



Question 9 - Add a variable to the dataset, which calculates the maximum total fat per type of restaurant and call it `max_total_fat`

```{r}

max_total_fat<-fastfood%>%group_by(restaurant)%>%mutate(max_total_fat=max(total_fat))%>%select(restaurant,max_total_fat)%>%ungroup()

```



Question 10 - Use observations for Mcdonalds to plot sugar variable against protein with `geom_point()` 


```{r} 

fastfod%>%filter(restaurant=="McDonalds")%>%ggplot(aes(x=restaurant, y=sugar)) + geom_point

```