---
title: "Assessment 1.1"
author: "Kishan Goonewardane s4647535"
date: "16/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Question 2 
# R Markdown editing 

Question 3 and 4
*R Markdown* is a markdown-based authoring syntax that blends the simplicity of Markdown with the mathematical programming language R. An R Markdown text or presentation intertwines calculation, performance, and written analysis, resulting in openness, **consistency**, and an implicit invitation to replicate.

Question 5
[links](https://rmarkdown.rstudio.com/lesson-8.html)

Question 6
```{r}
library(tidyverse)

fast_food<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```

Question 7
```{r}
fast_food%>%head(10)

calories<-fast_food$calories

```

Question 8
```{r}

library(dplyr)

fast_food%>%filter(calories > 1000)
```

Question 9
```{r}
`dont_eat_this`<-fast_food%>%filter(total_fat>40, total_carb>80)
```





